Tsbrowse: an interactive browser for Ancestral Recombination Graphs

### 2025-04-22 manuscript/paper.tex

\subsection{Inference of 1000 Genomes dataset (Suppl. Fig.
\ref{fig:Supplementary_Figure_2}, Suppl. Fig.
\ref{fig:Supplementary_Figure_3})} The 1000 Genomes dataset was downloaded from
\texttt{\url{https://ftp.1000genomes.ebi.ac.uk/vol1/ftp/data_collections/1000G_2504_high_coverage/working/20220422_3202_phased_SNV_INDEL_SV/}}.
Ancestral fasta sequences for chromosomes 17 and 20 (GRCh38) were downloaded
from the Ensembl database. Inference was performed with a Snakemake pipeline
(\texttt{\url{https://github.com/benjeffery/tsinfer-snakemake/}}) using
\texttt{tsinfer version 0.3.3} for the long arms of chromosome 17 and 20 after
filtering out duplicate variant positions, variants with missing or low quality
ancestral allele, singletons, n-1-tons and n-2-tons. Only bi-allelic SNPs were
included for inference. For the inference in Suppl. Fig.
\ref{fig:Supplementary_Figure_2}, all genomic regions were included. For the
inference in Suppl. Fig. \ref{fig:Supplementary_Figure_3}, genomic regions with
a site density lesser than 5 per kb were discarded. For Suppl. Fig.
\ref{fig:Supplementary_Figure_2}, \texttt{tsdate version 0.2.1} was used to
estimate the age of ancestral nodes with \textit{mutation rate = 1.29e-8},
setting all other parameters to default values.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{figures/SuppFig3.png}
    \caption{\textbf{A view of the Nodes page for a 1000 Genomes inference.} A
        screenshot of \texttt{tsbrowse}'s Nodes view for an inference of the long arm
        of chromosome 20 from the 1000 Genomes whole-genome sequencing dataset. At the
        top is a plot of node spans over time. The length of sequence that the nodes
        span is shown on the X axis, and the time of nodes is shown on the Y axis. The
        histogram at the bottom shows the distribution of node spans. }
    \label{fig:Supplementary_Figure_3}
\end{figure}

>>>>

\subsection{Inference of 1000 Genomes dataset (Suppl. Fig.
\ref{fig:Supplementary_Figure_2}, Suppl. Fig.
\ref{fig:Supplementary_Figure_3})} The 1000 Genomes dataset was downloaded from
\texttt{\url{https://ftp.1000genomes.ebi.ac.uk/vol1/ftp/data_collections/1000G_2504_high_coverage/working/20220422_3202_phased_SNV_INDEL_SV/}}.
The ancestral fasta sequence for chromosome 17 (GRCh38) was downloaded
from the Ensembl database. Inference was performed with a Snakemake pipeline
(\texttt{\url{https://github.com/benjeffery/tsinfer-snakemake/}}) using
\texttt{tsinfer version 0.3.3} for the long arm of chromosome 17 after
filtering out duplicate variant positions, variants with missing or low quality
ancestral allele, singletons, n-1-tons and n-2-tons. Only bi-allelic SNPs were
included for inference. For Suppl. Fig. \ref{fig:Supplementary_Figure_2}, 
\texttt{tsdate version 0.2.1} was used to estimate the age of ancestral nodes
 with \textit{mutation rate = 1.29e-8}, setting all other parameters to default 
 values.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{figures/SuppFig3.png}
    \caption{\textbf{A view of the Nodes page for a 1000 Genomes inference.} A
        screenshot of \texttt{tsbrowse}'s Nodes view for an inference of the long arm
        of chromosome 17 from the 1000 Genomes whole-genome sequencing dataset. At the
        top is a plot of node spans over time. The length of sequence that the nodes
        span is shown on the X axis, and the time of nodes is shown on the Y axis. The
        histogram at the bottom shows the distribution of node spans. }
    \label{fig:Supplementary_Figure_3}
\end{figure}
